%------------------------
% Shubh Resume Template
% Author: Shubham Kumar
% License: CC-BY-4.0
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{tikz}
\input{glyphtounicode}

% font options
\usepackage[sc]{mathpazo}
\linespread{1.05}  % palladio needs more leading (space between lines)
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}  % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% % sections formatting
% \titleformat{\section}{
%   \vspace{-4pt}\scshape\raggedright\large
% }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


% sections formatting
\titleformat{\section}{
  \vspace{-4pt}\large\centering\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



% ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% custom commands
\newcommand{\cvitem}[1]{
  \item\small{
    {#1\vspace{-2pt}}
  }
}

\newcommand{\cvheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvheadingstart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\cvheadingend}{\end{itemize}}
\newcommand{\cvitemstart}{\begin{itemize}\justifying}
\newcommand{\cvitemend}{\end{itemize}\vspace{-5pt}}

\newcommand{\cvskill}[2]{
  \textcolor{black}{\textbf{#1:}} {#2}\hfill \\
  % \foreach \x in {1,...,5}{%
  %   \space{\ifnumgreater{\x}{#2}{\color{black!80!white!20}}{\color{black}}\faSquare}}\par%
  % \vspace{-2pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\footnotesize$\bullet$}}$}

\begin{document}

% % contact information
% \begin{center}
%   \textbf{\LARGE\scshape Shubham Kumar} \\
%   \vspace{1pt}\small
%   \faAddressBook \href{mailto:}{ sshubhamk1@hotmail.com}
%   $\ \diamond\ $
%   \faMobile* +91 9877883408
%   $\ \diamond\ $
%   \faGithub  \href{https://github.com/sshubhamk1}{ github.com/sshubhamk1} \\
%   \faLinkedin \href{https://www.linkedin.com/in/sshubhamk1}{ linkedin.com/in/sshubhamk1}
%   $\ \diamond\ $
%   \faHouseUser \href{https://sshubhamk1.github.io}{ sshubhamk1.github.io}
% \end{center}


% contact information
\begin{center}
  \textbf{\LARGE\scshape Shubham Kumar} \\
  \vspace{1pt}\small
  \faAddressBook \href{mailto:}{ sshubhamk1@hotmail.com}
  % \textbullet{}
  \faMobile* +91 9877883408
  % \textbullet{}
  \faGithub  \href{https://github.com/sshubhamk1}{ github.com/sshubhamk1} \\
  \faLinkedin \href{https://www.linkedin.com/in/sshubhamk1}{ linkedin.com/in/sshubhamk1}
  % \textbullet{}
  \faHouseUser \href{https://sshubhamk1.github.io}{ sshubhamk1.github.io}
\end{center}



\section{Summary}
Experienced Software Engineer with 3+ years of expertise in designing and optimizing scalable backend systems and microservices architectures. Seeking an SDE 2 role to apply technical skills and leadership in delivering high-impact software solutions.

% \section{Technical Skills}
% \cvskill{Programming Language}{Python $\ \diamond\ $ Javascript $\ \diamond\ $ C/C++$\ \diamond\ $ Java}
% \cvskill{Web Development}{HTML$\ \diamond\ $ CSS $\ \diamond\ $\ Bootstrap $\ \diamond\ $ Javascript$\ \diamond\ $ ReactJS $\ \diamond\ $ Node.js $\ \diamond\ $ Django$\ \diamond\ $ Express.js}
% \cvskill{Database management}{SQL (MySQL, PostgreSQL) $\ \diamond\ $ NoSQL (MongoDB, Cassandra)}
% \cvskill{Additional Skills}{Git $\ \diamond\ $ Docker $\ \diamond\ $ AWS $\ \diamond\ $  GCP $\ \diamond\ $ REST API $\ \diamond\ $ Data Structures \& Algorithms $\ \diamond\ $ Object-Oriented Design $\ \diamond\ $ Microservice Architecture $\ \diamond\ $  Design Patterns $\ \diamond\ $ Web Security}
% % \vspace{2pt}


\section{Technical Skills}
\cvskill{Programming Language}{Python \textbullet{}  Javascript \textbullet{} C/C++ \textbullet{} Java}
\cvskill{Web Development}{HTML \textbullet{} CSS \textbullet{} Bootstrap \textbullet{} Javascript \textbullet{} ReactJS \textbullet{} Node.js \textbullet{}  Django \textbullet{} Express.js}
\cvskill{Database management}{SQL (MySQL, PostgreSQL) \textbullet{} NoSQL (MongoDB, Cassandra)}
\cvskill{Miscellaneous}{Git \textbullet{} Docker \textbullet{} AWS \textbullet{}  GCP \textbullet{} REST API \textbullet{} Data Structures \& Algorithms \textbullet{} Object-Oriented Design \textbullet{} Microservice Architecture \textbullet{}  Design Patterns \textbullet{} Web Security}
% \vspace{2pt}

\vspace{2pt}


\section{Professional Experience}
\cvheadingstart
  \cvheading
  {Scale AI}{San Francisco, California (Remote)}{Software Engineer (Contract)}{03/2024 - Present}
  \cvitemstart
 \cvitem{Enhanced code quality by reviewing 10k+ lines of AI-generated code for readability, correctness, and best practices alignment.}
 \cvitem{Refined AI models through 12 RLHF iterations, increasing solution efficiency and accuracy by 35\%.}
  % \cvitem{\textbf{Skills: } Python3, Pandas, Numpy, Matplotlib, scikit-learn}
  \cvitemend
  \cvheading
  {Techstat dynamics pvt limited}{Ludhiana, Punjab (Remote)}{Lead Software Engineer (FreeLancer)}{11/2023 - 02/2024}
  \cvitemstart
  \cvitem{Architected microservices, cutting deployment time by 30\% and boosting performance by 25\% through advanced data structures and algorithms.}
  \cvitem{Increased system responsiveness by 25\% through Redis Pub/Sub integration.}
  \cvitem{Upgraded performance by 30\% by implementing WebSocket between the portal and frontend.}
  % \cvitem{Streamlined microservices containerization using Docker Compose.}
  \cvitem{Increased system performance by 20\% through targeted performance testing and bottleneck resolution.}
  % \cvitem{\textbf{Skills: } Python3, Django, web socket, PostgreSQL, ReactJS, Redis, Nodejs, Nginx, Docker}
  \cvitemend
  \cvheading
    {Radisys Corporation}{Bangalore, Karnataka}
    {Senior Software Engineer, 5G Platform Team}{07/2021 - 11/2023}
  \cvitemstart
    \cvitem{Boosted JIO CCDU server performance by reducing startup/shutdown time by 50+ seconds, cutting server size by 72\%, and automating setup to minimize errors. Improved SysMon with customizable metrics, resolving memory leaks and refining CPU utilization metrics.}
    \cvitem{Led a team of five in a hackathon, driving feature discussions and ensuring code quality. Automated CCDU image building and updated open-source libraries with custom GCC flags and patches.}
    \cvitem{Designed and led startup scripts for ProcMon, ensuring compatibility and performance.}
    \cvitem{Streamlined CI/CD by automating Jenkins builds, CCDU image creation, and test case generation.}
    % \cvitem{\textbf{Skils: } Object-Oriented Design, High level Design, Draw.io, RHEL, Docker}
  \cvitemend
  Software Engineer, 5G Platform Team
  \cvitemstart
    \cvitem{Addressed issues in Process Monitor and System Monitor, including resolving date discrepancies in CentOS.}
    \cvitem{Generated comprehensive test cases for Process Monitor and System Monitor.}
    \cvitem{Led integration testing of Process Monitor with software upgrades and managed rollback tests with the OAM team.}
    % \cvitem{\textbf{Skills: } C/C++, Bash, Python, Linux, CentOS}
  \cvitemend



  \cvheading
    {Think201}{Bangalore, Karnataka (Remote)}
    {Software Engineer Intern, Web Application Backend Team}{09/2020 - 11/2020}
  \cvitemstart
    \cvitem{Built backend for web application using Node.js, including model schemas and APIs as per requirements.}
    % \cvitem{\textbf{Skills: } Node.js, Typescript, PostgreSQL, MongoDB, Express, Swagger, Postman}
  \cvitemend

  

\cvheadingend



\vspace{-5pt}



\section{Education}
\cvheadingstart
  \cvheading
    {National Institute of Technology Karnataka}{Surathkal, Karnataka}
    {M.Tech(Research) in Computer Science \& Engineering - Information Security}{08/2019 - 12/2022}
  % \cvheading
  %   {Lovely Professional University}{Phagwara, Punjab}
  %   {B.Tech in Computer Science \& Engineering}{09/2015 - 06/2019}
\cvheadingend

\section{Additional Projects}
\cvheadingstart


\cvheading {Real-Time Collaborative Document Editing Platform}{Bangalore, India}{Personal Project}{03/2024 - 07/2024}
\cvitemstart
\cvitem{Engineered a real-time document editing platform using Java (Spring Boot) with versioning, role-based access control, and JWT authentication (AWS Cognito).}
\cvitem{Integrated AWS OpenSearch for full-text search and AWS ElastiCache (Redis) for caching and session management.}
\cvitem{Enabled real-time updates with AWS MSK (Kafka) and multithreading for concurrent editing.}
\cvitem{Maintained data consistency with Hibernate ORM and ACID transactions; deployed on AWS EC2 with Auto Scaling and ELB.}
\cvitem{Monitored and logged activities using Log4j and AWS CloudWatch, ensuring high code quality through JUnit and Mockito testing.}
\cvitemend

  \cvheading
    {Network-Level Mitigation of Mirai Malware in IoT}{Surathkal, Karnataka}
    {Research Scholar, Information Security, NITK Surathkal}{12/2020 - 12/2021}
  \cvitemstart
  \cvitem{Researched and developed network-level mitigation strategies for Mirai malware in IoT environments, creating an isolated environment for demonstration.}
    \cvitem{Implemented effective malware mitigation solutions, publishing three papers on the findings.}
    % \cvitem{\textbf{Skills: } Python, Flask, Mysql, Docker, C, Golang, React.js, IoT, DDoS attacks}
  \cvitemend

\cvheadingend


\end{document}
